---
title: "R Notebook"
output: html_notebook
---

```{r libraries}
# Core Tidyverse
library(tidyverse)
library(glue)
library(forcats)

# Time Series
library(timetk)
library(tidyquant)
library(tibbletime)

# Visualization
library(cowplot)

# Preprocessing
library(recipes)

# Sampling / Accuracy
install.packages("yardstick")
library(rsample)
library(rolling_origin) 

# Modeling
library(keras)

```


```{r setup}
set.seed(1014)
options(digits = 3)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  dev = c("pdf", "png")
)

lappend <- function(lst, obj) {
  lst[[length(lst)+1]] <- obj
  return(lst)
}

fun_name = "sandbox"
options(dplyr.print_min = 6, dplyr.print_max = 6)
```

## 2.0 DATA
based on : http://www.business-science.io/timeseries-analysis/2018/04/18/keras-lstm-sunspots-time-series-prediction.html

The dataset, sunspot.month, is available for all of us (it ships with base R). It’s a ts class (not tidy), so we’ll convert to a tidy data set using the tk_tbl() function from timetk. We use this instead of as.tibble() from tibble to automatically preserve the time series index as a zoo yearmon index. Last, we’ll convert the zoo index to date using lubridate::as_date() (loaded with tidyquant) and then change to a tbl_time object to make time series operations easier.

```{r data}
sun_spots <- datasets::sunspot.month %>%
    tk_tbl() %>%
    mutate(index = as_date(index)) %>%
    as_tbl_time(index = index)

sun_spots
```

## 3.0 EXPLORATORY DATA ANALYSIS
The time series is long (265 years!). We can visualize the time series both full (265 years) and zoomed in on the first 50 years to get a feel for the series.

## 3.1 VISUALIZING SUNSPOT DATA WITH COWPLOT
We’ll make to ggplots and combine them using cowplot::plot_grid(). Note that for the zoomed in plot, we make use of tibbletime::time_filter(), which is an easy way to perform time-based filtering.

```{r explore, fig.width=10}

p1 <- sun_spots %>%
    ggplot(aes(index, value)) +
    geom_point(color = palette_light()[[1]], alpha = 0.5) +
    theme_tq() +
    labs(
        title = "From 1749 to 2013 (Full Data Set)"
    )

p2 <- sun_spots %>%
    filter_time("start" ~ "1800") %>%
    ggplot(aes(index, value)) +
    geom_line(color = palette_light()[[1]], alpha = 0.5) +
    geom_point(color = palette_light()[[1]]) +
    geom_smooth(method = "loess", span = 0.2, se = FALSE) +
    theme_tq() +
    labs(
        title = "1749 to 1800 (Zoomed In To Show Cycle)",
        caption = "datasets::sunspot.month"
    )

p_title <- ggdraw() + 
    draw_label("Sunspots", size = 18, fontface = "bold", colour = palette_light()[[1]])

plot_grid(p_title, p1, p2, ncol = 1, rel_heights = c(0.1, 1, 1))


```
At first glance, it looks like this series should be easy to predict. However, we can see that the cycle (10-year frequency) and amplitude (count of sunspots) seems to change at least between years 1780 and 1800. This creates some challenges.


## 3.2 EVALUATING THE ACF
The next thing we can do is determine whether or not an LSTM model may be a good approach. The LSTM will leverage autocorrelation to generate sequence predictions. Our goal is to produce a 10-year forecast using batch forecasting (a technique for creating a single forecast batch across the forecast region, which is in contrast to a single-prediction that is iteratively performed one or several steps into the future). The batch prediction will only work if the autocorrelation used is beyond ten years. Let’s inspect.

First, we need to review the Autocorrelation Function (ACF), which is the correlation between the time series of interest in lagged versions of itself. The acf() function from the stats library returns the ACF values for each lag as a plot. However, we’d like to get the ACF values as data so we can investigate the underlying data. To do so, we’ll create a custom function, tidy_acf(), to return the ACF values in a tidy tibble.

```{r acf_function}

tidy_acf <- function(data, value, lags = 0:20) {
    
    value_expr <- enquo(value)
    
    acf_values <- data %>%
        pull(value) %>%
        acf(lag.max = tail(lags, 1), plot = FALSE) %>%
        .$acf %>%
        .[,,1]
    
    ret <- tibble(acf = acf_values) %>%
        rowid_to_column(var = "lag") %>%
        mutate(lag = lag - 1) %>%
        filter(lag %in% lags)
    
    return(ret)
}


```
Next, let’s test the function out to make sure it works as intended. The function takes our tidy time series, extracts the value column, and returns the ACF values along with the associated lag in a tibble format. We have 601 autocorrelation (one for the time series and it’s 600 lags). All looks good.

```{r autocorrelation}

max_lag <- 12 * 50

sun_spots %>%
    tidy_acf(value, lags = 0:max_lag)

sun_spots %>%
    tidy_acf(value, lags = 0:max_lag) %>%
    ggplot(aes(lag, acf)) +
    geom_segment(aes(xend = lag, yend = 0), color = palette_light()[[1]]) +
    geom_vline(xintercept = 120, size = 3, color = palette_light()[[2]]) +
    annotate("text", label = "10 Year Mark", x = 130, y = 0.8, 
             color = palette_light()[[2]], size = 6, hjust = 0) +
    theme_tq() +
    labs(title = "ACF: Sunspots")

```

This is good news. We have autocorrelation in excess of 0.5 beyond lag 120 (the 10-year mark). We can theoretically use one of the high autocorrelation lags to develop an LSTM model.

```{r acf_plot}

sun_spots %>%
    tidy_acf(value, lags = 115:135) %>%
    ggplot(aes(lag, acf)) +
    geom_vline(xintercept = 120, size = 3, color = palette_light()[[2]]) +
    geom_segment(aes(xend = lag, yend = 0), color = palette_light()[[1]]) +
    geom_point(color = palette_light()[[1]], size = 2) +
    geom_label(aes(label = acf %>% round(2)), vjust = -1,
              color = palette_light()[[1]]) +
    annotate("text", label = "10 Year Mark", x = 121, y = 0.8, 
             color = palette_light()[[2]], size = 5, hjust = 0) +
    theme_tq() +
    labs(title = "ACF: Sunspots",
         subtitle = "Zoomed in on Lags 115 to 135")
```

Upon inspection, the optimal lag occurs at lag 125. This isn’t necessarily the one we will use since we have more to consider with batch forecasting with a Keras LSTM. With that said, here’s how you can filter() to get the best lag.
```{r lag_optimal} 

optimal_lag_setting <- sun_spots %>%
    tidy_acf(value, lags = 115:135) %>%
    filter(acf == max(acf)) %>%
    pull(lag)

optimal_lag_setting
```

##4.0 BACKTESTING: TIME SERIES CROSS VALIDATION
Cross validation is the process of developing models on sub-sampled data against a validation set with the goal of determining an expected accuracy level and error range. Time series is a bit different than non-sequential data when it comes to cross validation. Specifically, the time dependency on previous time samples must be preserved when developing a sampling plan. We can create a cross validation sampling plan using by offsetting the window used to select sequential sub-samples. In finance, this type of analysis is often called “Backtesting”, which takes a time series and splits it into multiple uninterupted sequences offset at various windows that can be tested for strategies on both current and past observations.

A recent development is the rsample package, which makes cross validation sampling plans very easy to implement. Further, the rsample package has Backtesting covered. The vignette, “Time Series Analysis Example”, describes a procedure that uses the rolling_origin() function to create samples designed for time series cross validation. We’ll use this approach.

#4.1 DEVELOPING A BACKTESTING STRATEGY
The sampling plan we create uses 50 years (initial = 12 x 50 samples) for the training set and ten years (assess = 12 x 10) for the testing (validation) set. We select a skip span of twenty years (skip = 12 x 20) to evenly distribute the samples into 11 sets that span the entire 265 years of sunspots history. Last, we select cumulative = FALSE to allow the origin to shift which ensures that models on more recent data are not given an unfair advantage (more observations) that those on less recent data. The tibble return contains the rolling_origin_resamples.

```{r backtesting}
periods_train <- 12 * 50
periods_test  <- 12 * 10
skip_span     <- 12 * 20

rolling_origin_resamples <- rolling_origin(
    sun_spots,
    initial    = periods_train,
    assess     = periods_test,
    cumulative = FALSE,
    skip       = skip_span
)

rolling_origin_resamples

```

##4.2 VISUALIZING THE BACKTESTING STRATEGY
We can visualize the resamples with two custom functions. The first, plot_split(), plots one of the resampling splits using ggplot2. Note that an expand_y_axis argument is added to expand the date range to the full sun_spots dataset date range. This will become useful when we visualize all plots together.


```{r plot_split}

?training()


# Plotting function for a single split
plot_split <- function(split, expand_y_axis = TRUE, alpha = 1, size = 1, base_size = 14) {
    
    # Manipulate data
    train_tbl <- training(split) %>%
        add_column(key = "training") 
    
    test_tbl  <- testing(split) %>%
        add_column(key = "testing") 
    
    data_manipulated <- bind_rows(train_tbl, test_tbl) %>%
        as_tbl_time(index = index) %>%
        mutate(key = fct_relevel(key, "training", "testing"))
        
    # Collect attributes
    train_time_summary <- train_tbl %>%
        tk_index() %>%
        tk_get_timeseries_summary()
    
    test_time_summary <- test_tbl %>%
        tk_index() %>%
        tk_get_timeseries_summary()
    
    # Visualize
    g <- data_manipulated %>%
        ggplot(aes(x = index, y = value, color = key)) +
        geom_line(size = size, alpha = alpha) +
        theme_tq(base_size = base_size) +
        scale_color_tq() +
        labs(
            title    = glue("Split: {split$id}"),
            subtitle = glue("{train_time_summary$start} to {test_time_summary$end}"),
            y = "", x = ""
        ) +
        theme(legend.position = "none") 
    
    if (expand_y_axis) {
        
        sun_spots_time_summary <- sun_spots %>% 
            tk_index() %>% 
            tk_get_timeseries_summary()
        
        g <- g +
            scale_x_date(limits = c(sun_spots_time_summary$start, 
                                    sun_spots_time_summary$end))
    }
    
    return(g)
}

#The plot_split() function takes one split (in this case Slice01), and returns a visual of the sampling strategy. We expand the axis to the range for the full dataset using expand_y_axis = TRUE.

rolling_origin_resamples$splits[[1]] %>%
    plot_split(expand_y_axis = TRUE) +
    theme(legend.position = "bottom")

```
The second function, plot_sampling_plan(), scales the plot_split() function to all of the samples using purrr and cowplot.
```{r plotting_backtesting, fig.width = 15}

# Plotting function that scales to all splits 
plot_sampling_plan <- function(sampling_tbl, expand_y_axis = TRUE, 
                               ncol = 3, alpha = 1, size = 1, base_size = 14, 
                               title = "Sampling Plan") {
    
    # Map plot_split() to sampling_tbl
    sampling_tbl_with_plots <- sampling_tbl %>%
        mutate(gg_plots = map(splits, plot_split, 
                              expand_y_axis = expand_y_axis,
                              alpha = alpha, base_size = base_size))
    
    # Make plots with cowplot
    plot_list <- sampling_tbl_with_plots$gg_plots 
    
    p_temp <- plot_list[[1]] + theme(legend.position = "bottom")
    legend <- get_legend(p_temp)
    
    p_body  <- plot_grid(plotlist = plot_list, ncol = ncol)
    
    p_title <- ggdraw() + 
        draw_label(title, size = 18, fontface = "bold", colour = palette_light()[[1]])
    
    g <- plot_grid(p_title, p_body, legend, ncol = 1, rel_heights = c(0.05, 1, 0.05))
    
    return(g)
    
}

#We can now visualize the ENTIRE BACKTESTING STRATEGY with plot_sampling_plan()! We can see how the sampling plan shifts the sampling window with each progressive slice of the train/test splits.

rolling_origin_resamples %>%
    plot_sampling_plan(expand_y_axis = T, ncol = 3, alpha = 1, size = 1, base_size = 10, 
                       title = "Backtesting Strategy: Rolling Origin Sampling Plan")


```
And, we can set expand_y_axis = FALSE to zoom in on the samples.
```{r plotting_backtesting2, fig.width = 15}
rolling_origin_resamples %>%
    plot_sampling_plan(expand_y_axis = F, ncol = 3, alpha = 1, size = 1, base_size = 10, 
                       title = "Backtesting Strategy: Zoomed In")


```
We’ll use this Backtesting Strategy (11 samples from one time series each with 50/10 split in years and a 20 year offset) when testing the veracity of the LSTM model on the sunspots dataset.


##5.0 MODELING THE KERAS STATEFUL LSTM MODEL
To begin, we’ll develop a single Keras Stateful LSTM model on a single sample from the Backtesting Strategy. We’ll then scale the model to all samples to investigate/validate the modeling performance.

5.1 SINGLE LSTM
For the single LSTM model, we’ll select and visualize the split for the most recent time sample/slice (Slice11). The 11th split contains the most recent data.

```{r single_split}

split <- rolling_origin_resamples$splits[[11]]
split_id <- rolling_origin_resamples$id[[11]]

plot_split(split, expand_y_axis = FALSE, size = 0.5) +
    theme(legend.position = "bottom") +
    ggtitle(glue("Split: {split_id}"))

```

##5.1.2 DATA SETUP
First, let’s combine the training and testing data sets into a single data set with a column key that specifies what set they came from (either “training” or “testing)”. Note that the tbl_time object will need to have the index re-specified during the bind_rows() step, but this issue should be corrected in dplyr soon (please upvote it so RStudio focuses on it).

```{r data_setup}
df_trn <- training(split)
df_tst <- testing(split)

df <- bind_rows(
    df_trn %>% add_column(key = "training"),
    df_tst %>% add_column(key = "testing")
) %>% 
    as_tbl_time(index = index)

```

5.1.3 PREPROCESSING WITH RECIPES
The LSTM algorithm requires the input data to be centered and scaled. We can preprocess the data using the recipes package. We’ll use a combination of step_sqrt to transform the data and reduce the presence of outliers and step_center and step_scale to center and scale the data. The data is processed/transformed using the bake() function.
```{r preprocess}

rec_obj <- recipe(value ~ ., df) %>%
    step_sqrt(value) %>%
    step_center(value) %>%
    step_scale(value) %>%
    prep()

df_processed_tbl <- bake(rec_obj, df)

df_processed_tbl

#Next, let’s capture the center/scale history so we can invert the center and scaling after modeling. The square-root transformation can be inverted by squaring the inverted center/scale values.

center_history <- rec_obj$steps[[2]]$means["value"]
scale_history  <- rec_obj$steps[[3]]$sds["value"]

c("center" = center_history, "scale" = scale_history)


```

#5.1.4 LSTM PLAN
We need a plan for building the LSTM. First, a couple PRO TIPS with LSTM’s:

Tensor Format:

Predictors (X) must be a 3D Array with dimensions: [samples, timesteps, features]: The first dimension is the length of values, the second is the number of time steps (lags), and the third is the number of predictors (1 if univariate or n if multivariate)
Outcomes/Targets (y) must be a 2D Array with dimensions: [samples, timesteps]: The first dimension is the length of values and the second is the number of time steps (lags)
Training/Testing:

The training and testing length must be evenly divisible (e.g. training length / testing length must be a whole number)
Batch Size:

The batch size is the number of training examples in one forward/backward pass of a RNN before a weight update
The batch size must be evenly divisible into both the training an testing lengths (e.g. training length / batch size and testing length / batch size must both be whole numbers)
Time Steps:

A time step is the number of lags included in the training/testing set
For our example, our we use a single lag
Epochs:

The epochs are the total number of forward/backward pass iterations
Typically more improves model performance unless overfitting occurs at which time the validation accuracy/loss will not improve
Taking this in, we can come up with a plan. We’ll select a prediction of window 120 months (10 years) or the length of our test set. The best correlation occurs at 125, but this is not evenly divisible by the forecasting range. We could increase the forecast horizon, but this offers a minimal increase in autocorrelation. We can select a batch size of 40 units which evenly divides into the number of testing and training observations. We select time steps = 1, which is because we are only using one lag. Finally, we set epochs = 300, but this will need to be adjusted to balance the bias/variance tradeoff.

```{r model_inputs}

# Model inputs
lag_setting  <- 120 # = nrow(df_tst)
batch_size   <- 40
train_length <- 440
tsteps       <- 1
epochs       <- 300

```

#5.1.5 2D AND 3D TRAIN/TEST ARRAYS
We can then setup the training and testing sets in the correct format (arrays) as follows. Remember, LSTM’s need 3D arrays for predictors (X) and 2D arrays for outcomes/targets (y).

```{r reshaping_data_for_lstm}
# Training Set
lag_train_tbl <- df_processed_tbl %>%
    mutate(value_lag = lag(value, n = lag_setting)) %>% 
    filter(!is.na(value_lag)) %>% 
    filter(key == "training") %>% 
    tail(train_length)

x_train_vec <- lag_train_tbl$value_lag
x_train_arr <- array(data = x_train_vec, dim = c(length(x_train_vec), 1, 1))

y_train_vec <- lag_train_tbl$value
y_train_arr <- array(data = y_train_vec, dim = c(length(y_train_vec), 1))

# Testing Set
lag_test_tbl <- df_processed_tbl %>%
    mutate(
        value_lag = lag(value, n = lag_setting)
    ) %>%
    filter(!is.na(value_lag)) %>%
    filter(key == "testing")

x_test_vec <- lag_test_tbl$value_lag
x_test_arr <- array(data = x_test_vec, dim = c(length(x_test_vec), 1, 1))

y_test_vec <- lag_test_tbl$value
y_test_arr <- array(data = y_test_vec, dim = c(length(y_test_vec), 1))

```
#5.1.6 BUILDING THE LSTM MODEL
We can build an LSTM model using the keras_model_sequential() and adding layers like stacking bricks. We’ll use two LSTM layers each with 50 units. The first LSTM layer takes the required input shape, which is the [time steps, number of features]. The batch size is just our batch size. We set the first layer to return_sequences = TRUE and stateful = TRUE. The second layer is the same with the exception of batch_size, which only needs to be specified in the first layer, and return_sequences = FALSE which does not return the time stamp dimension (2D shape is returned versus a 3D shape from the first LSTM). We tack on a layer_dense(units = 1), which is the standard ending to a keras sequential model. Last, we compile() using the loss = "mae" and the popular optimizer = "adam".

```{r simple_lstm}

model <- keras_model_sequential()

model %>%
    layer_lstm(units            = 50, 
               input_shape      = c(tsteps, 1), 
               batch_size       = batch_size,
               return_sequences = TRUE, 
               stateful         = TRUE) %>% 
    layer_lstm(units            = 50, 
               return_sequences = FALSE, 
               stateful         = TRUE) %>% 
    layer_dense(units = 1)

model %>% 
    compile(loss = 'mae', optimizer = 'adam')

model


```

#5.1.7 FITTING THE LSTM MODEL
Next, we can fit our stateful LSTM using a for loop (we do this to manually reset states). This will take a minute or so for 300 epochs to run. We set shuffle = FALSE to preserve sequences, and we manually reset the states after each epoch using reset_states().

```{r fitting_simple_lstm}
  
for (i in 1:epochs) {
      model %>% fit(x          = x_train_arr, 
                    y          = y_train_arr, 
                    batch_size = batch_size,
                    epochs     = 1, 
                    verbose    = 1, 
                    shuffle    = FALSE)
      
      model %>% reset_states()
      cat("Epoch: ", i)
      
  }

```


#5.1.8 PREDICTING USING THE LSTM MODEL
We can then make predictions on the test set, x_test_arr, using the predict() function. We can retransform our predictions using the scale_history and center_history, which were previously saved and then squaring the result. Finally, we combine the predictions with the original data in one column using reduce() and a custom time_bind_rows() function.


```{r predicting_lstm}
# Make Predictions
pred_out <- model %>% 
    predict(x_test_arr, batch_size = batch_size) %>%
    .[,1] 

# Retransform values
pred_tbl <- tibble(
    index   = lag_test_tbl$index,
    value   = (pred_out * scale_history + center_history)^2
) 

# Combine actual data with predictions
tbl_1 <- df_trn %>%
    add_column(key = "actual")

tbl_2 <- df_tst %>%
    add_column(key = "actual")

tbl_3 <- pred_tbl %>%
    add_column(key = "predict")

# Create time_bind_rows() to solve dplyr issue
time_bind_rows <- function(data_1, data_2, index) {
    index_expr <- enquo(index)
    bind_rows(data_1, data_2) %>%
        as_tbl_time(index = !! index_expr)
}

ret <- list(tbl_1, tbl_2, tbl_3) %>%
    reduce(time_bind_rows, index = index) %>%
    arrange(key, index) %>%
    mutate(key = as_factor(key))

ret
```

#5.1.9 ASSESSING PERFORMANCE OF THE LSTM ON A SINGLE SPLIT
We can use the yardstick package to assess performance using the rmse() function, which returns the root mean squared error (RMSE). Our data is in the long format (optimal format for visualizing with ggplot2), so we’ll create a wrapper function calc_rmse() that processes the data into the format needed for yardstick::rmse().

```{r rmse}
calc_rmse <- function(prediction_tbl) {
    
    rmse_calculation <- function(data) {
        data %>%
            spread(key = key, value = value) %>%
            select(-index) %>%
            filter(!is.na(predict)) %>%
            rename(
                truth    = actual,
                estimate = predict
            ) %>%
            rmse(truth, estimate)
    }
    
    safe_rmse <- possibly(rmse_calculation, otherwise = NA)
    
    safe_rmse(prediction_tbl)
        
}

```

5.1.10 VISUALIZING THE SINGLE PREDICTION
Next, we make a plotting function, plot_prediction(), using ggplot2 to visualize the results for a single sample.
```{r visualizing_lstm_prediction}

# Setup single plot function
plot_prediction <- function(data, id, alpha = 1, size = 2, base_size = 14) {
    
    rmse_val <- calc_rmse(data)
    
    g <- data %>%
        ggplot(aes(index, value, color = key)) +
        geom_point(alpha = alpha, size = size) + 
        theme_tq(base_size = base_size) +
        scale_color_tq() +
        theme(legend.position = "none") +
        labs(
            title = glue("{id}, RMSE: {round(rmse_val, digits = 1)}"),
            x = "", y = ""
        )
    
    return(g)
}


# We can test out the plotting function setting the id = split_id, which is “Slice11”.
ret %>% 
    plot_prediction(id = split_id, alpha = 0.65) +
    theme(legend.position = "bottom")


```
5.2 BACKTESTING THE LSTM ON ALL ELEVEN SAMPLES
Once we have the LSTM working for one sample, scaling to all 11 is relatively simple. We just need to create an prediction function that can be mapped to the sampling plan data contained in rolling_origin_resamples.

5.2.1 CREATING AN LSTM PREDICTION FUNCTION
This step looks intimidating, but it’s actually straightforward. We copy the code from Section 5.1 into a function. We’ll make it a safe function, which is a good practice for any long-running mapping processes to prevent a single failure from stopping the entire process.

```{r predict_big}
predict_keras_lstm <- function(split, epochs = 300, ...) {
    
    lstm_prediction <- function(split, epochs, ...) {
        
        # 5.1.2 Data Setup
        df_trn <- training(split)
        df_tst <- testing(split)
        
        df <- bind_rows(
            df_trn %>% add_column(key = "training"),
            df_tst %>% add_column(key = "testing")
        ) %>% 
            as_tbl_time(index = index)
        
        # 5.1.3 Preprocessing
        rec_obj <- recipe(value ~ ., df) %>%
            step_sqrt(value) %>%
            step_center(value) %>%
            step_scale(value) %>%
            prep()
        
        df_processed_tbl <- bake(rec_obj, df)
        
        center_history <- rec_obj$steps[[2]]$means["value"]
        scale_history  <- rec_obj$steps[[3]]$sds["value"]
        
        # 5.1.4 LSTM Plan
        lag_setting  <- 120 # = nrow(df_tst)
        batch_size   <- 40
        train_length <- 440
        tsteps       <- 1
        epochs       <- epochs
        
        # 5.1.5 Train/Test Setup
        lag_train_tbl <- df_processed_tbl %>%
            mutate(value_lag = lag(value, n = lag_setting)) %>%
            filter(!is.na(value_lag)) %>%
            filter(key == "training") %>%
            tail(train_length)
        
        x_train_vec <- lag_train_tbl$value_lag
        x_train_arr <- array(data = x_train_vec, dim = c(length(x_train_vec), 1, 1))
        
        y_train_vec <- lag_train_tbl$value
        y_train_arr <- array(data = y_train_vec, dim = c(length(y_train_vec), 1))
        
        lag_test_tbl <- df_processed_tbl %>%
            mutate(
                value_lag = lag(value, n = lag_setting)
            ) %>%
            filter(!is.na(value_lag)) %>%
            filter(key == "testing")
        
        x_test_vec <- lag_test_tbl$value_lag
        x_test_arr <- array(data = x_test_vec, dim = c(length(x_test_vec), 1, 1))
        
        y_test_vec <- lag_test_tbl$value
        y_test_arr <- array(data = y_test_vec, dim = c(length(y_test_vec), 1))
                
        # 5.1.6 LSTM Model
        model <- keras_model_sequential()

        model %>%
            layer_lstm(units            = 50, 
                       input_shape      = c(tsteps, 1), 
                       batch_size       = batch_size,
                       return_sequences = TRUE, 
                       stateful         = TRUE) %>% 
            layer_lstm(units            = 50, 
                       return_sequences = FALSE, 
                       stateful         = TRUE) %>% 
            layer_dense(units = 1)
        
        model %>% 
            compile(loss = 'mae', optimizer = 'adam')
        
        # 5.1.7 Fitting LSTM
        for (i in 1:epochs) {
            model %>% fit(x          = x_train_arr, 
                          y          = y_train_arr, 
                          batch_size = batch_size,
                          epochs     = 1, 
                          verbose    = 0, 
                          shuffle    = FALSE)
            
            model %>% reset_states()
            cat("Epoch: ", i)
            
        }
        
        # 5.1.8 Predict and Return Tidy Data
        # Make Predictions
        pred_out <- model %>% 
            predict(x_test_arr, batch_size = batch_size) %>%
            .[,1] 
        
        # Retransform values
        pred_tbl <- tibble(
            index   = lag_test_tbl$index,
            value   = (pred_out * scale_history + center_history)^2
        ) 
        
        # Combine actual data with predictions
        tbl_1 <- df_trn %>%
            add_column(key = "actual")
        
        tbl_2 <- df_tst %>%
            add_column(key = "actual")
        
        tbl_3 <- pred_tbl %>%
            add_column(key = "predict")
        
        # Create time_bind_rows() to solve dplyr issue
        time_bind_rows <- function(data_1, data_2, index) {
            index_expr <- enquo(index)
            bind_rows(data_1, data_2) %>%
                as_tbl_time(index = !! index_expr)
        }
        
        ret <- list(tbl_1, tbl_2, tbl_3) %>%
            reduce(time_bind_rows, index = index) %>%
            arrange(key, index) %>%
            mutate(key = as_factor(key))

        return(ret)
        
    }
    
    safe_lstm <- possibly(lstm_prediction, otherwise = NA)
    
    safe_lstm(split, epochs, ...)
    
}

#We can test the custom predict_keras_lstm() function out with 10 epochs. It returns the data in long format with “actual” and “predict” values in the key column.

predict_keras_lstm(split, epochs = 10)

```

# 5.2.2 MAPPING THE LSTM PREDICTION FUNCTION OVER THE 11 SAMPLES
With the predict_keras_lstm() function in hand that works on one split, we can now map to all samples using a mutate() and map() combo. The predictions will be stored in a “list” column called “predict”. Note that this will take 5-10 minutes or so to complete.
```{r predict_11_splits}

sample_predictions_lstm_tbl <- rolling_origin_resamples %>%
     mutate(predict = map(splits, predict_keras_lstm, epochs = 300))

```
5.2.3 ASSESSING THE BACKTESTED PERFORMANCE
We can assess the RMSE by mapping the calc_rmse() function to the “predict” column.

```{r rmse_all}
sample_rmse_tbl <- sample_predictions_lstm_tbl %>%
    mutate(rmse = map_dbl(predict, calc_rmse)) %>%
    select(id, rmse)


sample_rmse_tbl %>%
    summarize(
        mean_rmse = mean(rmse),
        sd_rmse   = sd(rmse)
    )


sample_rmse_tbl %>%
    ggplot(aes(rmse)) +
    geom_histogram(aes(y = ..density..), fill = palette_light()[[1]], bins = 16) +
    geom_density(fill = palette_light()[[1]], alpha = 0.5) +
    theme_tq() +
    ggtitle("Histogram of RMSE")


```

5.2.4 VISUALIZING THE BACKTEST RESULTS
We can create a plot_predictions() function that returns one plot with the predictions for the entire set of 11 backtesting samples!!!
```{r viz_backtesting_all, fig.width=15}
plot_predictions <- function(sampling_tbl, predictions_col, 
                             ncol = 3, alpha = 1, size = 2, base_size = 14,
                             title = "Backtested Predictions") {
    
    predictions_col_expr <- enquo(predictions_col)
    
    # Map plot_split() to sampling_tbl
    sampling_tbl_with_plots <- sampling_tbl %>%
        mutate(gg_plots = map2(!! predictions_col_expr, id, 
                               .f        = plot_prediction, 
                               alpha     = alpha, 
                               size      = size, 
                               base_size = base_size)) 
    
    # Make plots with cowplot
    plot_list <- sampling_tbl_with_plots$gg_plots 
    
    p_temp <- plot_list[[1]] + theme(legend.position = "bottom")
    legend <- get_legend(p_temp)
    
    p_body  <- plot_grid(plotlist = plot_list, ncol = ncol)
    
    
    
    p_title <- ggdraw() + 
        draw_label(title, size = 18, fontface = "bold", colour = palette_light()[[1]])
    
    g <- plot_grid(p_title, p_body, legend, ncol = 1, rel_heights = c(0.05, 1, 0.05))
    
    return(g)
    
}

sample_predictions_lstm_tbl %>%
    plot_predictions(predictions_col = predict, alpha = 0.5, size = 1, base_size = 10,
                     title = "Keras Stateful LSTM: Backtested Predictions")

```

5.3 PREDICTING THE NEXT 10 YEARS
We can predict the next 10 years by adjusting the prediction function to work with the full data set. A new function, predict_keras_lstm_future(), is created that predicts the next 120 time steps (or ten years).

```{r prediction_all}
predict_keras_lstm_future <- function(data, epochs = 300, ...) {
    
    lstm_prediction <- function(data, epochs, ...) {
        
        # 5.1.2 Data Setup (MODIFIED)
        df <- data
        
        # 5.1.3 Preprocessing
        rec_obj <- recipe(value ~ ., df) %>%
            step_sqrt(value) %>%
            step_center(value) %>%
            step_scale(value) %>%
            prep()
        
        df_processed_tbl <- bake(rec_obj, df)
        
        center_history <- rec_obj$steps[[2]]$means["value"]
        scale_history  <- rec_obj$steps[[3]]$sds["value"]
        
        # 5.1.4 LSTM Plan
        lag_setting  <- 120 # = nrow(df_tst)
        batch_size   <- 40
        train_length <- 440
        tsteps       <- 1
        epochs       <- epochs
        
        # 5.1.5 Train Setup (MODIFIED)
        lag_train_tbl <- df_processed_tbl %>%
            mutate(value_lag = lag(value, n = lag_setting)) %>%
            filter(!is.na(value_lag)) %>%
            tail(train_length)
        
        x_train_vec <- lag_train_tbl$value_lag
        x_train_arr <- array(data = x_train_vec, dim = c(length(x_train_vec), 1, 1))
        
        y_train_vec <- lag_train_tbl$value
        y_train_arr <- array(data = y_train_vec, dim = c(length(y_train_vec), 1))
        
        x_test_vec <- y_train_vec %>% tail(lag_setting)
        x_test_arr <- array(data = x_test_vec, dim = c(length(x_test_vec), 1, 1))
                
        # 5.1.6 LSTM Model
        model <- keras_model_sequential()

        model %>%
            layer_lstm(units            = 50, 
                       input_shape      = c(tsteps, 1), 
                       batch_size       = batch_size,
                       return_sequences = TRUE, 
                       stateful         = TRUE) %>% 
            layer_lstm(units            = 50, 
                       return_sequences = FALSE, 
                       stateful         = TRUE) %>% 
            layer_dense(units = 1)
        
        model %>% 
            compile(loss = 'mae', optimizer = 'adam')
        
        # 5.1.7 Fitting LSTM
        for (i in 1:epochs) {
            model %>% fit(x          = x_train_arr, 
                          y          = y_train_arr, 
                          batch_size = batch_size,
                          epochs     = 1, 
                          verbose    = 1, 
                          shuffle    = FALSE)
            
            model %>% reset_states()
            cat("Epoch: ", i)
            
        }
        
        # 5.1.8 Predict and Return Tidy Data (MODIFIED)
        # Make Predictions
        pred_out <- model %>% 
            predict(x_test_arr, batch_size = batch_size) %>%
            .[,1] 
        
        # Make future index using tk_make_future_timeseries()
        idx <- data %>%
            tk_index() %>%
            tk_make_future_timeseries(n_future = lag_setting)
        
        # Retransform values
        pred_tbl <- tibble(
            index   = idx,
            value   = (pred_out * scale_history + center_history)^2
        )
        
        # Combine actual data with predictions
        tbl_1 <- df %>%
            add_column(key = "actual")

        tbl_3 <- pred_tbl %>%
            add_column(key = "predict")

        # Create time_bind_rows() to solve dplyr issue
        time_bind_rows <- function(data_1, data_2, index) {
            index_expr <- enquo(index)
            bind_rows(data_1, data_2) %>%
                as_tbl_time(index = !! index_expr)
        }

        ret <- list(tbl_1, tbl_3) %>%
            reduce(time_bind_rows, index = index) %>%
            arrange(key, index) %>%
            mutate(key = as_factor(key))

        return(ret)
        
    }
    
    safe_lstm <- possibly(lstm_prediction, otherwise = NA)
    
    safe_lstm(data, epochs, ...)
    
}

#Next, run predict_keras_lstm_future() on the sun_spots data set.
future_sun_spots_tbl <- predict_keras_lstm_future(sun_spots, epochs = 300)


```
Last, we can visualize the forecast with the plot_prediction() function, setting id = NULL. We can use filter_time() to zoom in on the dataset since 1900.

```{r final_predictions}

future_sun_spots_tbl %>%
    filter_time("1900" ~ "end") %>%
    plot_prediction(id = NULL, alpha = 0.4, size = 1.5) +
    theme(legend.position = "bottom") +
    ggtitle("Sunspots: Ten Year Forecast", subtitle = "Forecast Horizon: 2013 - 2023")

```

